### 2022-09-17 main/chapter_searches.tex
add energy-based modelling citations

From such $\log$ ratios, a little rearrangement recovers the individual
probabilities through the logistic function:
\begin{equation}
\label{eqn:searches_logistic}
\prob{S}{d} = \frac{1}{1 + e^{-\Delta(d)}}
.
\end{equation}
Physically, this is analogous to the Boltzmann distribution where the energy
of each model is its negative $\log$ probability, with unit inverse
temperature~\cite{
pmlr-v2-ranzato07a,
skilling2017david
}.
With multiple models in play, it is also called the `softmax'
function~\cite{MurphyKevinP.2012Mlap}.

>>>>

From such $\log$ ratios, a little rearrangement recovers the individual
probabilities through the logistic function:
\begin{equation}
\label{eqn:searches_logistic}
\prob{S}{d} = \frac{1}{1 + e^{-\Delta(d)}}
.
\end{equation}
Physically, this is analogous to the Boltzmann distribution where the energy
of each model is its negative $\log$ probability, with unit inverse
temperature~\cite{
pmlr-v2-ranzato07a,
skilling2017david,
lecun-06,
pmlr-v2-ranzato07a
}.
With multiple models in play, it is also called the `softmax'
function~\cite{MurphyKevinP.2012Mlap}.
